\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
%\usepackage{xcolor}
\usepackage{color}% http://ctan.org/pkg/color

\usepackage[pdftex,colorlinks=false,pdfborderstyle={/S/U/W 1},urlbordercolor={0 0 0}]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% font: arial
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
% font: helvetica-style
%\usepackage{tgheros}
%\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
% See icons: http://mirrors.ibiblio.org/CTAN/fonts/fontawesome/doc/fontawesome.pdf
\begin{center}
    \textbf{\Huge Niccol\`o Zuppichini} \\ \vspace{5pt}
    \small \faPhone* \texttt{+41 76 275 07 06} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{niccolo.zuppichini@gmail.com} \hspace{1pt}  \\
    \hspace{1pt} \faLinkedin \hspace{2pt} \texttt{\href{https://www.linkedin.com/in/niccolo-zuppichini}{www.linkedin.com/in/niccolo-zuppichini}} \hspace{1pt} \\
%    \hspace{1pt} \faGithub \hspace{2pt} \texttt{rage997} \hspace{1pt} $|$ \\
    \hspace{1pt} \faHome \hspace{2pt}\texttt{\href{https://rage997.github.io/}{rage997.github.io}}   \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Bellinzona, Switzerland}
    \\ \vspace{-3pt}
\end{center}

% --------- Education -----------

\section {EDUCATION}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Universit\`a della Svizzera Italiana}{September 2019 -- June 2022}
      {Master in Computational Science}{Lugano, CH}
      	\resumeItemListStart
      	\resumeItem 
            {\textbf{Thesis}: \href{https://github.com/Rage997/MasterThesis}{Invasive species modeling via relational event models.}}
    	\resumeItem {\textbf{Coursework}: Stochastic Optimization, Numerical Analysis, PDE/ODE, Deep Learning.}
    	\resumeItem{\textbf{GPA}: 7.66}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
\resumeSubHeadingListStart
    \resumeSubheading
      {Universit\`a della Svizzera Italiana}{September 2016 -- June 2019}
      {Bachelor in Informatics}{Lugano, CH}
      	\resumeItemListStart
      	\resumeItem 
            {\textbf{Project}: \href{https://github.com/Rage997/BachelorProject}{A robust pipeline to process 3D objects.}}
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Machine Learning.}
    	 \resumeItem{\textbf{GPA}: 7.45}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
  
%-----------Mindcraft-----------
  \resumeSubheading
      {\href{https://mndcr.com/}{Mindcraft}}{October 2022 -- Today}
      {Senior Software Engineer}{Bern, CH}
      \resumeItemListStart
       \resumeItem{Implementing optimized services for 3D scanning, 3D data hosting and 3D data publishing.}
        \resumeItem{Partecipate in the development of Meshvalley, a web platform capable of rendering and publishing 3D content in photorealistic quality.}
        	\resumeItem{Actively working on advanced algorithms to optimize \href{https://meshvalley.com/}{Meshvalley} custom WebGL rendering engine.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://panua.ch/}{Panua}}{July 2022 -- Present}
      {Web Developer / DevOps Engineer (Freelance)}{Lugano, CH}
      \resumeItemListStart
      \resumeItem{Collaborate with Panua's team on an hourly basis, providing expertise in Web Development, DevOps and Software Engineering.}
      \resumeItem{Implemented a software to generate, validate, and authenticate users' machine fingerprints to prevent the piracy of Panua Technologies Software, enhancing the security of the company's products.}
      \resumeItem{Ensuring high availability and performance of Panua's software platforms.}
      \resumeItem{Develop automated deployment and testing pipelines using Docker, improving the efficiency and reliability of software releases.}
    \resumeItemListEnd

%-----------HEGIAS-----------
    \resumeSubheading
      {\href{https://hegias.com/en/}{Hegias}}{September 2018 -- September 2020}
      {Software Engineer | DevOps Manager}{Lugano \& Zurich, CH}
      \resumeItemListStart
       \resumeItem{Led Agile team of 5 developers to continuous deployment and increased productivity by 20\% by pair programming.}
        \resumeItem{Responsible for the Unix server infrastructure capable of handling thousands of clients’ request.}
        \resumeItem{Independently solved the performance issues of the rendering engine by implementing advanced rendering techniques, 3D objects compression and a machine learning 3D object classification.}
        \resumeItem{Decreased the running time of the 3D objects processing pipeline by more than 250\% by distributing the server infrastructure on different nodes.}
        \resumeItem{The company reached more than 2.1 milion Swiss Francs in funding and was selected  as one of the top \href{https://www.eu-startups.com/2019/02/10-swiss-startups-to-watch-in-2019/}{10 startup to look after.}}
%         \resumeItem{Technologies used: Unity, Numpy, PyMesh, Node.js, MongoDB, three.js, WebGL}
         %        \resumeItem{Spearheaded product development of a new lab workflow tool, leading to a 40\% increase in efficiency; \\ shadowed 10 core users, iterated on design docs, and implemented the solution with one engineer}
      \resumeItemListEnd
      
%-----------CS-----------
    \resumeSubheading
      {\href{https://www.ics.usi.ch/}{Institute of Computational Science}}{June 2018 -- September. 2018}
      {Junior Researcher}{Lugano, CH}
      \resumeItemListStart
        \resumeItem{Contributed to the development of \href{https://bitbucket.org/zulianp/utopia/src/master/}{Utopia}, a state-of-the-art High-Performance C++ parallel computing library to solve non-linear high-dimensional problems.}
        \resumeItem{Full source code available on the \href{https://bitbucket.org/zulianp/utopia/src/master/}{Project Maintainer's repository}}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
     \resumeProjectHeading
         {\textbf{Autoregressive model study on the crypto market.}} {2022}
         \resumeItemListStart
           \resumeItem{A study on cryptocurrencies casual relationships and their casual direction using an Autoregressive model (VAR).}
           \resumeItem{The main research interest was in detecting the "big players" that dictate the directions of the market using advanced statistical tools.}
           \resumeItem{Full source code can be found on my personal \href{https://github.com/Rage997/VarModelCrypto}{GitHub profile}.}
         \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{3D Spectral Segmentation}}{2021}
          \resumeItemListStart
            \resumeItem{Designed and implemented a \href{https://www.blender.org}{Blender}'s add-on to automatically detect 3D objects features using  a custom Spectral Segmentation algorithm.}
            \resumeItem{The add-on received more than 200 downloads alongside a lot of positive feedback.}
			\resumeItem{Full source code can be found on my personal \href{https://github.com/Rage997/Spectral-Clustering-mesh-segmentation}{GitHub profile}.}

          \resumeItemListEnd
          

%      \resumeProjectHeading
%         {\textbf{CommonIntern}}{Sept. 2019 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Built a Python script to automatically apply to jobs on Glassdoor using BeautifulSoup and Selenium}
%            \resumeItem{\textbf{500 stars on \href{https://github.com/harshibar/common-intern}{\myuline {GitHub}}}; featured on {\href{https://hackaday.com/2020/05/30/job-application-script-automates-the-boring-stuff-with-python}{\myuline {Hackaday}}}; made the front page of {\href {https://www.reddit.com/r/Python/comments/gpaegj/i_was_tired_of_opening_100s_of_tabs_for/?utm_source=share}{\myuline {r/python}}} and {\href {https://www.reddit.com/r/programming/comments/dcmbzx/i_was_tired_of_opening_100s_of_tabs_for/}{\myuline {r/programming}}}}
%          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
% \begin{itemize}[leftmargin=0in, label={}]
%    \small{\item{
%     \textbf{Languages} {: Python, JavaScript (React.js), HTML/CSS, SQL (PostgreSQL, MySQL)}\vspace{2pt} \\
%     \textbf{Tools}     {: Figma, Notion, Jira, Trello, Miro, Google Analytics, GitHub, DaVinci Resolve, OBS}
%    }}
% \end{itemize}
%\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
%\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\begin{minipage}[ht]{0.48\textwidth}
\textbf{Programming languages:} \\
Python C++, C\#, OO \\ Javascript, Rust
\vspace{1em}

\textbf{Frameworks:} \\
Numpy, Pandas, Scikit-learn, PyTorch, Cuda, OpenMPI, \\ 
NodeJS, mongoDB, WebGL, ThreeJS
%ThreeJS, WebGL, D3, \\
%Moralis, Metamask
%D3.js, three.js, WebGL \\

%OpenCV, OpenMPI
\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
\textbf{Deployments:} \\
AWS, Kubernetes, Rancher, Docker, Linux

\vspace{1em}
\textbf{Languages:} \\
Italian: Native \\
{\bf English}: {\bf Full Professional proficiency}\\
%French: Professional proficiency

\end{minipage}


%-------------------------------------------
\end{document}
